A Global Genome-wide Scan with Optimal Cutoff Mining for Emerging Biomarkers in Head and Neck Squamous Cell Carcinoma

### 2021-02-25 main.tex
TCIA

\subsubsection{TCPA validation}
TCGA pathology Deep learning TCPA
數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。

@@

Updated: August 31, 2020
%
TMA by deep learning (CNN) mRNA expression associated with pathological images

recurrent neural network for NLP
%氨基酸或DNA等序列的使用可說是相當普遍，由於序列可視為一種具有隱性結構的語言，因此自然語言處理模型所採用的架構便可運用在理解並生成生物醫學領域的序列。

\subsubsection{Holistic cancer care} % by epigenetic control (placebo), person-central approach, PCA

@@

Lipton introduced mind-brain-body system.
Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
 In a state of fear, the brain releases chemicals associated with fear, which are stress hormones and inflammatory agents.
dopamine, oxytocin, vasopressin, and growth hormone will be released by central nerve system in response to the perception of love.

@@

PCA and ECA
Carl Rogers: Carl Rogers' person-centered theory
the therapist is providing the appropriate social-environmental conditions \cite{Rogers1957}.\cite{Joseph2004}\cite{Griffiths2013}
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers\cite{Rogers1957}.
The research implication is to investigate the relationship between the client’s intrinsic motivation to explore his or her trauma-related thoughts and feelings and the nature of the therapeutic relationship as defined by the six conditions\cite{Rogers1957}.
Dealing with negative emotions. As the client feels intense negative emotions of fear, despair, sadness and so on, it is not the client-centred therapist’s task to try and remove these feelings: The task is simply to stay with the client’s experiences. T he research implication is to investigate the necessity and sufficiency of the six conditions.

@@

%%%%%% carcinomgenesis
95\% of cognitive behavior runs on subconscious program:

7\% 對於健康有不良影響 => 但是惡劣競爭下的生存技能
Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage. These programs were acquired from other people, not from ourselves. Again, being subconscious, these programs are occurring without conscious recognition and awareness. 
It effects on epigenetic regulation.

@@

*** TCPA with deep learning: gene expression on pathological section, or digital tissue microarray, TMA
佩戴可監測心率、體溫、血壓及其他關鍵數據的裝置，醫師也因此能夠獲得更多資料以更深入瞭解患者的病情，不再依靠病人的回憶進行判斷，診斷的準確性也會隨之提升。

在生物醫學領域，氨基酸或DNA等序列的使用可說是相當普遍，由於序列可視為一種具有隱性結構的語言，因此自然語言處理模型所採用的架構便可運用在理解並生成生物醫學領域的序列。

>>>>

\subsubsection{TCIA validation}
https://wiki.cancerimagingarchive.net/display/Public/TCGA-HNSC
https://cancer.digitalslidearchive.org/#!/CDSA/hnsc/TCGA-BA-4076/TCGA-BA-4076-01A-01-BS1?slide=TCGA-BA-4076-01A-01-BS1.4aef481c-f634-4ffc-9fb3-609f59a8caf9.svs
TCGA Pathology Images (TCIA) Deep learning
數位模擬，能讓臨床醫師和研究人員更快速了解細胞成長後的狀況，而不是花費時間等待細胞的培養。
image-based phenotypes and their underlying genomic data 
https://www.biorxiv.org/content/10.1101/2020.03.10.985887v1.full
https://github.com/Serian1992/ImgBio.

The Stanford Tissue Microarray Database (TMAD; x http://tma.stanford.edu) 
https://tma.im/cgi-bin/ontologyBrowser.pl?anchor=C34447

@@

Updated: August 31, 2020
%
TMA by deep learning (CNN) mRNA expression associated with pathological images
*** TCGA Pathology Images with deep learning: gene expression on pathological section, or digital tissue microarray, TMA
recurrent neural network for NLP

佩戴可監測心率、體溫、血壓及其他關鍵數據的裝置，醫師也因此能夠獲得更多資料以更深入瞭解患者的病情，不再依靠病人的回憶進行判斷，診斷的準確性也會隨之提升。

%在生物醫學領域，氨基酸或DNA等序列的使用可說是相當普遍，由於序列可視為一種具有隱性結構的語言，因此自然語言處理模型所採用的架構便可運用在理解並生成生物醫學領域的序列。

\subsubsection{Holistic cancer care} 
% by epigenetic control (placebo/nocebo), Bruce Lipton introduced mind-brain-body system.
% person-central approach, PCA; Cullen, Carl Rogers

@@

%%
Bruce Lipton introduced mind-brain-body system.
Lipton 1992, epinephrine and histamine signals in endothelium, %心智作用
 In a state of fear, the brain releases chemicals associated with fear, which are stress hormones and inflammatory agents.
dopamine, oxytocin, vasopressin, and growth hormone will be released by central nerve system in response to the perception of love.

@@

%%%
PCA and ECA
Carl Rogers: Carl Rogers' person-centered theory
the therapist is providing the appropriate social-environmental conditions \cite{Rogers1957}.\cite{Joseph2004}\cite{Griffiths2013}
Person-centred theory holds that the innate tendency towards growth and development is facilitated by the six conditions described by Rogers\cite{Rogers1957}.
The research implication is to investigate the relationship between the client’s intrinsic motivation to explore his or her trauma-related thoughts and feelings and the nature of the therapeutic relationship as defined by the six conditions\cite{Rogers1957}.
Dealing with negative emotions. As the client feels intense negative emotions of fear, despair, sadness and so on, it is not the client-centred therapist’s task to try and remove these feelings: The task is simply to stay with the client’s experiences. T he research implication is to investigate the necessity and sufficiency of the six conditions.

@@

%%%%%% carcinogenesis
mind-brain-body axis: subconscious fear -> inflammatory and stress hormones -> DNA/methylation mutation/mRNA expression alteration -> carcinogenesis of cancer.
95\% of cognitive behavior runs on subconscious program:

7\% 對於健康有不良影響 => 卻是惡劣競爭下的生存技能
Of the downloaded behaviors acquired before age 7, the vast majority—70\% or more—are programs of limitation, disempowerment, and self-sabotage. These programs were acquired from other people, not from ourselves. Again, being subconscious, these programs are occurring without conscious recognition and awareness. 
It effects on epigenetic regulation.

@@
